A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-10-29 paper/elsarticle/elsarticle-template.tex
paper

\section{Evaluation}
We evaluate our approach by using a 960 pixel~$\times$~600 pixel image of the TU Wien logo (cf.\ Figure \ref{fig:warp}) to augment 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Wien, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace, absent of projective distortions, and with the same metric dimensions of 50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~$\times$~600; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis if aspect ratio is to be preserved.}. All experiments were carried out by the same technician, experienced in both approaches.

>>>>

\section{Evaluation}
We evaluate our approach by using a 960 pixel~$\times$~600 pixel image of the TU Wien logo (cf.\ Figure \ref{fig:warp}) to augment 15 locations across the floorspace at the Pilotfabrik\footnote{\url{https://www.pilotfabrik.at/}} of TU Wien, a collaborative space for research on Industry 4.0 topics situated in Vienna, Austria. We contrast our approach with a baseline approach involving manual keystone correction, by aiming with both approaches to place the same image for each location aligned with the principal axes of the floorspace (i.e., the yellow and red lines in Figure~\ref{fig:eval}(b)), absent of projective distortions, and with the same metric dimensions of 50~cm~$\times$~31.25~cm\footnote{The dimensions in pixels of the image we project are 960~$\times$~600; we chose for our experiments to set the projected metric length of the horizontal axis of the image to 50~cm, which implies 31.25~cm for the vertical axis if aspect ratio is to be preserved.}. All experiments were carried out by the same technician, experienced in both approaches.
